### 2019-08-23 lower.tex
Future directions

@@

  \maciek{ToDo: check all off-by-one errors}
  \maciek{ToDo: check if the existence of $b_1$ was considered in all calculations}

>>>>

  \maciek{Warning! This proof requires still major rewrite before submission!}
  \maciek{The argument of connecting the length of sequence and the number of merged singletons should be stated as an auxiliary lemma.}
  \maciek{Maybe we do not need to construct $I_2$ and then $I_2'$: we can construct $I_2'$ on-the-fly and bound its length. However, the subtracting argument (as it is written now) is quite simple.}
  \maciek{ToDo: (one) figure containing: input $I_1$, cluster $D$, growing components $v^C_i$, and the ``searched area (by ALG)'' (in searching for $d_1, d_2$)}

  \maciek{ToDo: check all off-by-one errors, especially this one: check if the existence of $b_1$ in one of the clusters was considered in all calculations}

@@
